---
title: "Getting Started with mathhammr"
author: "Peter D Smits"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r message = FALSE}
if (!require(devtools)) {
    install.packages('devtools')
}
devtools::install_github('psmits/mathhammr')
```

```{r message = FALSE}
library(dplyr)
library(magrittr)
library(purrr)
library(tidyr)
library(ggplot2)
library(mathhammr)
```

```{r}
# 5 man squad of space marines shot a 5 man squad of chaos space marines with bolters at > 12" away.
hits <- to_attack(n= 5, skill = 3)
print(hits)

wounds <- to_wound(n = hits, str = 4, tgh = 4)
print(wounds)

damage <- to_save(n = wounds, sv = 3, ap = 0)
print(damage)

```

Let's try that 1000 times.
```{r}
hits_many <- replicate(1000, to_attack(n = 5, skill = 3))
wounds_many <- map_dbl(hits_many, ~ to_wound(n = .x, str = 4, tgh = 4))
damage_many <- map_dbl(wounds_many, ~ to_save(n = .x, sv = 3, ap = 0))

results <- tibble(hits = hits_many,
                  wounds = wounds_many,
                  damage = damage_many) # damage on a bolter
results %>%
  gather(key = 'key', value = 'value') %>%
  mutate(key = case_when(key == 'hits' ~ 'Successful hit rolls',
                         key == 'wounds' ~ 'Successful wound rolls',
                         key == 'damage' ~ 'Unsaved wound rolls')) %>%
  ggplot() +
  geom_bar(aes(x = value, fill = key)) +
  facet_wrap(key ~ .) +
  labs(x = 'Result', y = 'Count') +
  theme(legend.position = 'none') +
  NULL
```


How about something more complicated. 30 Shoota boyz at a Rhino. Remembering Dakka, Dakka, Dakka.
```{r}
hits_boyz <- replicate(1000, to_attack(n = 2 * 30, skill = 5, explode = 6))
wounds_boyz <- map_dbl(hits_boyz, ~ to_wound(n = .x, str = 4, tgh = 7))
damage_boyz <- map_dbl(wounds_boyz, ~ to_save(n = .x, sv = 3, ap = 0))

results <- tibble(hits = hits_boyz,
                  wounds = wounds_boyz,
                  damage = damage_boyz* 1) # damage on a bolter
results %>%
  gather(key = 'key', value = 'value') %>%
  mutate(key = case_when(key == 'hits' ~ 'Successful hit rolls',
                         key == 'wounds' ~ 'Successful wound rolls',
                         key == 'damage' ~ 'Unsaved wound rolls')) %>%
  ggplot() +
  geom_bar(aes(x = value, fill = key)) +
  geom_vline(xintercept = 10, colour = 'black') +
  facet_wrap(key ~ .) +
  labs(x = 'Result', y = 'Count') +
  theme(legend.position = 'none') +
  NULL

# and percent of simulations where boyz kill the rhino?
kill_percent <- (sum(damage_boyz >= 10) / length(damage_boyz)) * 100
print(kill_percent)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
